Dependently Typed Multi-stage Calculus

### 2019-11-20 slides/main.tex
Writing a page on LTP.
Explaing Hanada&Igarashi.

>>>>

\begin{frame}[fragile]{\LTP [Hanada\&Igarashi'14]}
    Multi-stage calculus with Cross Stage Persistence (CSP)
    \begin{table}
        \begin{tabular}{ c | c | c }
            & MetaOCaml & \LTP \\
            \hline
            Make code & \verb| let a = .<(1+2)>.| & \( \textbf{let } a = \TB_\alpha (1 + 2) \) \\
            Embed code & \verb| .<(.~a)+(.~a)>.| & \( (\TB_\alpha (\TBL_\alpha a + \TBL_\alpha a)) \) \\
            Run code & \verb| run .<(1+2)>.| & \( \textbf{run } (\TB_\alpha (1 + 2)) \) \\
            Code type & \verb| int code | & \( \TW_\alpha \text{Int} \)
        \end{tabular}
    \end{table}
\end{frame}
